---
title: "test-fanny"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## avocados
https://www.kaggle.com/neuromusic/avocado-prices

do some eda, generate a couple of interesting viz to show gary on tuesday  

```{r}
library(tidyverse)
library(scales)
library(janitor)
library(lubridate)
theme_set(theme_light())
```



```{r rawdata}

avocado <- read_csv("../avocado/avocado.csv") %>% 
  select(-X1) %>% 
  clean_names() %>% 
  mutate(year = year(as.Date(as.character(year), format = "%Y")))

avocado %>% View()
```

```{r}
avocado %>% 
  group_by(year) %>% 
  summarise(total_vol_per_year = sum(total_volume)) %>% 
  ggplot(aes(group=year, total_vol_per_year)) +
  geom_boxplot()
```

Looks like there's equally as many conventional and organic avocado sales recorded in each time category.  
```{r}
ggplot(avocado) +
  geom_bar(mapping = aes(x=type))
```

```{r}
avocado %>% 
  count(type)
```

Looks like all regions are equally as represented in this data set. Note how California is an entire state but other places like Atlanta and Boston are large metropolitan regions.  
```{r}
avocado %>% 
  count(region) %>% 
  arrange(desc(n))
```


Regions with most avocado sales of all-time
```{r}
avocado %>% 
  group_by(region, total_volume) %>% 
  summarise(total_volume, total_vol_by_region = n())
# %>% 
  # arrange(desc(total_vol_by_region))
  
```



How does the average price change over time?
```{r}
# plot(avocados_raw$Date, avocados_raw$AveragePrice)
ggplot(avocados, aes(Date, AveragePrice)) + geom_line()
```

Let's aggregate by year: 
```{r}

avocados %>% group_by(month=floor_date(date, "month")) %>%
   summarize(vol_by_mon=sum())

```







```{r}


```


Is there a difference between PLUs?
```{r}
ggplot(avocados, aes())

```

